Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-18 qhtv2.tex
FNR

One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^m \FP_i$, and similarly for $\FNR_n$.

@@

	Finally this filter does not make any mistake, as the dictionary $D$ keeps an exact tract of how many times each element was present in the sliding window.
\end{proof}
The dependence on $\log_2 |\Gamma|$ can be droped, at the cost of allowing 
errors:
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.

@@

\paragraph{Pseudocode.}
We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}. We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$. The \texttt{subfilters} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.

@@

	\begin{algorithmic}[1]
	\Function{Lookup}{$e$}
		\For{$i$ from $0$ to $L-1$}
			\If{subfilters[i]$.\mathsf{Lookup(e)}$}
				\State \Return $\DUPLICATE$
			\EndIf
		\EndFor
		\State \Return \UNSEEN
	\EndFunction
	\item[]
	\end{algorithmic}

@@

\subsubsection{Probability of False Negative}\label{sub:fnr}
\begin{theorem}
	\label{thm:queue-pfn}
	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
	\begin{align*}
	\FN_{\mathcal Q, m}^w 
	= & \left[p_c\FN_{\mathcal F,c} + \left(1-p_c\right)\left(1-\FP_{\mathcal F,c}\right)\right]^{L-1} \\
	 \times & \left[p_{m\bmod c}\FN_{\mathcal F,m\bmod c} + \left(1-p_{m\bmod c}\right)\left(1-\FP_{\mathcal F,m\bmod c}\right)\right]
	\end{align*}
	where $\bmod$ is the modulo operator, $\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
	\begin{equation*}
		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w}.
	\end{equation*}
\end{theorem}

@@

\todo[TODO]

>>>>

One can observe that $\FPR_n = \frac{1}{n}\sum_{i=1}^n \FP_i$, and similarly for $\FNR_n$.

@@

	Finally this filter does not make any mistake, as every positive has a witness in $Q$ and any negative is absent from the last $w$ elements.
\end{proof}
The dependence on $\log_2 |\Gamma|$ can be droped, at the cost of allowing 
errors:
\begin{theorem}
	Let $w \in \mathbb N$. Let $M \simeq 2w\log_2w$, then the sliding window DDP can be solved with almost no error using $M$ bits of memory.

@@

\paragraph{Pseudocode.}
We give a brief pseudo-code of the queuing filter's functions \textsf{Lookup} and \textsf{Insert}, as well as a \textsf{Setup} function for initialisation, in \ref{alg:queueing}. We introduced for simplicity a constructor $\mathcal F.\textsf{Setup}$ that takes as input an integer $M$ and outputs an initialized empty filter $\mathcal F$ of size at most $M$. The \texttt{subfilter} is a FIFO that has a \texttt{pop} and \texttt{push\_first} operations, which respectevely removes the last element in the queue or inserts a new item in first  position.

@@

	\begin{algorithmic}[1]
	\Function{Lookup}{$e$}
		\For{$i$ from $0$ to $L-1$}
			\If{subfilter[i]$.\mathsf{Lookup(e)}$}
				\State \Return $\DUPLICATE$
			\EndIf
		\EndFor
		\State \Return \UNSEEN
	\EndFunction
	\item[]
	\end{algorithmic}

@@

\subsubsection{Probability of False Negative}\label{sub:fnr}
\begin{theorem}
	\label{thm:queue-pfn}
	Let $\FN_{\mathcal Q, m}^w$ be the probability of false negative of $\mathcal Q$ after $m > w$ insertions on a sliding window of size $w = cL$, we have
	\begin{equation}
	\FN_{\mathcal Q, m}^w 
	=  u_c^{L-1} u_{m \bmod c}
	\end{equation}
	where $\bmod$ is the modulo operator, and we have introduced the short-hand notation $u_\eta= p_{\eta}\FN_{\mathcal F,\eta} + \left(1-p_{\eta}\right)\left(1-\FP_{\mathcal F,\eta}\right)$ where 
	$\FN_{\mathcal F,m}$ is the probability of false negative of any subfilter $\mathcal F$ after $m$ insertions, and
	\begin{equation*}
		p_m = \frac{1-\left(1-\frac 1{|\Gamma|}\right)^m}{1-\left(1-\frac 1{|\Gamma|}\right)^w} \approx \frac{m}{w}.
	\end{equation*}
\end{theorem}

@@

\begin{align*}
	\FPR_{\mathcal Q, cn}^w
	& = \frac{1}{cn} \sum_{k=1}^{cn} \FP_{\mathcal Q, k}^w 
	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, k + \ell}^w 
	 = \frac1c \sum_{\ell = 0}^{c-1} \FP_{\mathcal Q, \ell}^w \\
	& = \frac1c \sum_{\ell = 0}^{c-1}  1 - (1 - \FP_{\mathcal F, c})^{L-1}(1 - \FP_{\mathcal F}, \ell) \\
	& = 1 -  (1 - \FP_{\mathcal F, c})^{L-1}\sum_{\ell = 0}^{c-1} \FP_{\mathcal F, \ell}
\end{align*}

\begin{align*}
	\FNR_{\mathcal Q, cn}^w 
	& = \frac{1}{cn} \sum_{k=1}^{cn} \FN_{\mathcal Q, k}^w 
	 = \frac{1}{cn} \sum_{k=1}^{n} \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, k + \ell}^w 
	= \frac1c \sum_{\ell = 0}^{c-1} \FN_{\mathcal Q, \ell}^w \\
	& = \frac1c \sum_{\ell = 0}^{c-1} u_c^{L-1} u_{\ell} 
	 = \frac{u_c^{L-1}}{c}  \sum_{\ell = 0}^{c-1}u_\ell
\end{align*}
